---
title: "Self-Driving Cars, How Safe Are They?"
author: "Trevor Tang, Jenna Moon-Earle, Sukyung Tae, Yeji Kim"
date: "12/1/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this file for?

* This file will eventually become your project report for **P02: Exploratory Data Analysis**. Specifically, you will write rmarkdown to report your exploratory data analysis.

* Please see Canvas for more details.

```{r, echo = FALSE, include = FALSE}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)

# SOURCE FILES HERE PLEASE!

source("../source/chart1.R")
```

---

### Summary

Value 1: Calculate the companies with the most ADS and ADAS crashes in `summary.R`

---

### Table

---

### Charts 1: ADAS / ADS Crashes Per Location
```{r crash_comparison, fig.height = 5, fig.width = 10, fig.align = "center", echo = FALSE}
ADAS_crash_location_map
ADS_crash_location_map
```
```{r manufacturer_crash, fig.height = 8, fig.width = 10, fig.align = "center", echo = FALSE}
crashes_per_manufacturer
```
The purpose of this map is to observe where and how many crashes are happening in locations around the United States. Most crashes seem to happen in California based on the large and dark red circles found there (particularly in Los Angeles), but also in Texas and New York. 

---

### Chart 2:

---

### Chart 3: