---
title: "Self-Driving Cars, How Safe Are They?"
author: "Trevor Tang, Jenna Moon-Earle, Sukyung Tae, Yeji Kim"
date: "12/1/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this file for?

* This file will eventually become your project report for **P02: Exploratory Data Analysis**. Specifically, you will write rmarkdown to report your exploratory data analysis.

* Please see Canvas for more details.

```{r, echo = FALSE, include = FALSE}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)

# SOURCE FILES HERE PLEASE!

source("../source/chart1.R")
source("../source/chart2.R")
source("../source/chart3.R")
source("../source/summary.R")
```

---

### Summary

A summary of the ADAS and ADS datasets are as follows: <br>
- **Number of observations in ADAS dataset**: `r summary_info$num_observations_ADAS` <br>
- **Number of observations in ADS dataset**: `r summary_info$num_observations_ADS` <br>
- **Company with most ADAS crashes**: `r summary_info$most_cars_ADAS$Make`; `r summary_info$most_cars_ADAS$total_crashes` crashes <br>
- **Company with most ADS crashes**: `r summary_info$most_cars_ADS$Make`; `r summary_info$most_cars_ADS$total_crashes` crashes <br>
- **Model with most ADAS crashes**: `r summary_info$most_model_crashes_ADAS$Model`;
`r summary_info$most_model_crashes_ADAS$total_crashes` crashes <br>
- **Model with most ADS crashes**: `r summary_info$most_model_crashes_ADS$Model`;
`r summary_info$most_model_crashes_ADS$total_crashes` crashes


---

### Table

---

### Charts 1: ADAS / ADS Crashes Per Location
```{r crash_comparison, fig.height = 5, fig.width = 10, fig.align = "center", echo = FALSE}
ADAS_crash_location_map
ADS_crash_location_map
```
```{r manufacturer_crash, fig.height = 8, fig.width = 10, fig.align = "center", echo = FALSE}
crashes_per_manufacturer
```
The purpose of this map is to observe where and how many crashes are happening in locations around the United States. Most crashes seem to happen in California based on the large and dark red circles found there (particularly in Los Angeles), but also in Texas and New York. 

---

### Chart 2: Types of Car Crahses in ADAS vs ADS
```{r fig.height = 8, fig.width = 8, fig.align = "center", echo = FALSE}
adas_type_pie
ads_type_pie
```
The pie chart illustrates what types of car crashes are most prevalent in ADAS and ADS in the United States. Most cases are unknown in ADAS whereas the top 3 in ADS are passenger cars, SUVs, and pickup trucks. 
---

### Chart 3:
```{r fig.height = 8, fig.width = 10, fig.align = "center", echo = FALSE}
ADAS_roadway_type
ADS_roadway_type
```
The bar graph depicts which roadway types are most prevalent in the crashes of ADAS and ADS in the United States. It is seen that the most crashes for ADAS happens on the highway, while it is on the intersection for ADS. 
---