---
title: "Self-Driving Cars, How Safe Are They?"
author: "Trevor Tang, Jenna Moon-Earle, Sukyung Tae, Yeji Kim"
date: "12/1/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)

# SOURCE FILES HERE PLEASE!

source("../source/chart1.R")
source("../source/chart2.R")
source("../source/chart3.R")
source("../source/summary.R")
source("../source/table.R")
```

---

### Summary

A summary of the ADAS and ADS datasets are as follows: <br>
- **Number of observations in ADAS dataset**: `r summary_info$num_observations_ADAS` <br>
- **Number of observations in ADS dataset**: `r summary_info$num_observations_ADS` <br>
- **Company with most ADAS crashes**: `r summary_info$most_cars_ADAS$Make`; `r summary_info$most_cars_ADAS$total_crashes` crashes <br>
- **Company with most ADS crashes**: `r summary_info$most_cars_ADS$Make`; `r summary_info$most_cars_ADS$total_crashes` crashes <br>
- **Model with most ADAS crashes**: `r summary_info$most_model_crashes_ADAS$Model`;
`r summary_info$most_model_crashes_ADAS$total_crashes` crashes <br>
- **Model with most ADS crashes**: `r summary_info$most_model_crashes_ADS$Model`;
`r summary_info$most_model_crashes_ADS$total_crashes` crashes


---

### Table
```{r fig.height = 8, fig.width= 8, fig.align = "center", echo = FALSE}
ai_ADAS_surface
ai_ADS_surface
```
These tables show ...

---

### Charts 1: ADAS / ADS Crashes Per Location
```{r crash_comparison, fig.height = 5, fig.width = 10, fig.align = "center", echo = FALSE}
ADAS_crash_location_map
ADS_crash_location_map
```
The purpose of these maps are to observe where and how many crashes are happening in locations around the United States. Most crashes seem to happen in California based on the large and dark red circles found there (particularly in Los Angeles), but also in Texas and New York. The results might be linked to higher populations and manufacturers in these states. **You can hover over the map to get information on the city and total number of crashes there**

---

### Chart 2: Types of Car Crashes in ADAS vs ADS
```{r pie, fig.height = 8, fig.width = 8, fig.align = "center", echo = FALSE}
adas_pie_chart
ads_pie_chart
```
The pie chart illustrates what types of car crashes are most prevalent in ADAS and ADS in the United States. Most cases in ADAS are with fixed objects and vehicles whereas the top 3 in ADS are passenger cars, SUVs, and pickup trucks. This makes sense since most of these vehicles are driven on busy roads where other vehicles are common. 

---

### Chart 3:
```{r fig.height = 8, fig.width = 10, fig.align = "center", echo = FALSE}
ADAS_roadway_type
ADS_roadway_type
```
The bar graph depicts which roadway types are most prevalent in the crashes of ADAS and ADS in the United States. It is seen that the most crashes for ADAS happens on the highway, while it is on the intersection for ADS. The ADAS roadway types might be the result that drivers like to turn on ADAS most likely when they are on highways. For ADS, it might mean that these cars struggle to identify red lights.
